An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-15 paper/main.tex
update result2.tex
extract abstract from main.tex, update abstract

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{lmodern}
\usepackage{pgffor}

@@

@@

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}

%{Zhenjiang Hu\inst{1}\orcidID{0000-0002-9034-205X}}
%{Robert Gl\"{u}ck\inst{2}\orcideID{0000-0001-6990-3935}}
%{Kanae Tsushima\inst{3}\orcidID{}}
%{Bach-Trong Nguyen\inst{3}\orcidID{}}
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%15--250 words.
  Bidirectional transformation (BX) is a solution of view update problems and widely used for synchronizing data. Its semantics and correctness are researched well, but the evaluation efficiency is not considered well. As a first attempt we consider efficiency of evaluation in this work. To improve evaluation efficiency, we focus on the evaluation of BX compositions, because its evaluation often causes redundant evaluations. 
  For evaluating BX compositions efficiently, we introduce two memoization strategies. The first strategy, minBigul\_m, uses so simple memoization, but it works well for many BX programs. This keeps the evaluated results in a table and reuse them.  A disadvantage of this is cost for saving to a table and searching. When the inputs are large, the evaluation time becomes slow. To treat large inputs, we introduce the second approach, xpg, that uses tupling and some optimization techniques. In this approach we shrink the size of the evaluated results and keep them in a closure. The experiments of these strategies show the following results: the original strategy is faster for right assoc compositions, minBiGUL\_m is faster for not-large inputs and xpg is faster for large inputs.

 % We show experimental results for several BX programs with simple inputs and large inputs.

@@

\input{3.pg.tex}

\input{4.cpg.tex}

\input{5.kpg.tex}

\input{6.xpg.tex}

@@

\input{9.conclusion}

@@

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{lmodern}
\usepackage{pgffor}
\usepackage{schemata}

@@

\newcommand{\putm}[3]{put_m \, [\![#1]\!] \ #2 \ #3}
\newcommand{\putminline}[1]{put_m \, [\![#1]\!]}
\newcommand{\getm}[2]{get_m \, [\![#1]\!] \ #2}
\newcommand{\getminline}[1]{get_m \, [\![#1]\!]}

\newcommand{\getmh}[2]{get_{mh} \, [\![#1]\!] \ #2}
\newcommand{\getmhinline}[1]{get_{mh} \, [\![#1]\!]}

@@

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}

%{Zhenjiang Hu\inst{1}\orcidID{0000-0002-9034-205X}}
%{Robert Gl\"{u}ck\inst{2}\orcideID{0000-0001-6990-3935}}
%{Kanae Tsushima\inst{3}\orcidID{}}
%{Bach-Trong Nguyen\inst{3}\orcidID{0000-0002-6342-6020}}
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%15--250 words.
 \input{0.abst.tex}
 % We show experimental results for several BX programs with simple inputs and large inputs.

@@

\input{3.minbigul_m.tex}

\input{4.xpg.tex}

@@

\input{9.conclusion.tex}

@@

\input{result2.tex}
